Escape Analysis and Specialization in a Tracing JIT

### 2010-09-28 talk/pepm2011/paper.tex
minimally fix an XXX

XXX object model and its reflection in traces (e.g. guard\_class before each method call)

@@

If the function is executed using the tracing JIT, with \texttt{y} being a
\texttt{BoxedInteger}, the produced trace looks like
Figure~\ref{fig:unopt-trace}. The operations in the trace are shown indented to
correspond to the stack level of the function that contains the traced
operation. The trace also shows the inefficiencies of \texttt{f} clearly, if one
looks at the number of \texttt{new}, \texttt{set/getfield} and
\texttt{guard\_class} operations.

>>>>

@@

If the function is executed using the tracing JIT, with \texttt{y} being a
\texttt{BoxedInteger}, the produced trace looks like
Figure~\ref{fig:unopt-trace}. The operations in the trace are shown indented to
correspond to the stack level of the function that contains the traced
operation. The trace also shows the inefficiencies of \texttt{f} clearly, if one
looks at the number of \texttt{new} (corresponding to object creation),
\texttt{set/getfield} (corresponding to attribute reads/writes) and
\texttt{guard\_class} operations (corresponding to method calls).
